TO FIND

### 2013-05-16 ms.tex
First sentence of the paragraph re. effects of landscape structure on relative importance of processes

The instrumentalism view of neutral theory raises the question of why should it
be a satisfying approximation despite knowing the pieces are wrong? We see two
potential answers to this question. A first answer might be that stochasticity
of various origins can blur the deterministic differences among species and
promote the ecological drift \parencite{Gravel2011}. Much has been said the
existence of demographic stochasticity, some ecologists even arguing that
neutral models impede progress in community ecology by hidding niche differences
\parencite{Clark2012}, and we therefore will keep this discussion for other
papers. The second answer is that dispersal and historical contingencies might
have a much more profound impact on species distribution \parencite{Bahn2007}
and ecological dynamics. The debate over the equivalence assumption and
demographic stochasticity has perhaps overlook the recognition of how much
dispersal influence community assembly.

@@

>>>>

The instrumentalist view of neutral theory raises the question of why it should
be a satisfying approximation despite knowing the pieces are wrong? We see two
potential answers to this question. A first answer might be that stochasticity
of various origins can blur the deterministic differences among species and
promote the ecological drift \parencite{Gravel2011}. Much has been said the
existence of demographic stochasticity, some ecologists even arguing that
neutral models impede progress in community ecology by hidding niche differences
\parencite{Clark2012}, and we therefore will keep this discussion for other
papers. The second answer is that dispersal and historical contingencies might
have a much more profound impact on species distribution \parencite{Bahn2007}
and ecological dynamics. The debate over the equivalence assumption and
demographic stochasticity has perhaps overlook the recognition of how much
dispersal influence community assembly.

@@

Our results point to an important, although often overlooked, consequence of
neutral dynamics. Emerging properties of a community (i.e. the number of
species, but also their spatial distribution and co-occurence at different local
patches), are affected by the dispersal structure.
